Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-05-03 mu/article/article.tex
Thery section added for layer contribution.

@@

\subsection{Fixing velocity.}\label{sec:theory-fixvel}
Considering that we have 2D structures we fixed the velocity in the $xy$ plane
along $x$ and $y$ directions and we define $|\mathcal{V}^{\mathrm{a}}|$ as
\begin{equation}\label{eq:va-mag}
|\mathcal{V}^{\mathrm{a}}| = 
\sqrt {
(\mathcal{V}^{\mathrm{ax}})^{2} +
(\mathcal{V}^{\mathrm{ay}})^{2} +
(\mathcal{V}^{\mathrm{az}})^{2} 
},
\end{equation}
and the corresponding polar and azimuthal angles $\theta$ and $\varphi$ as
\begin{align}
\theta  =& \cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}}
{|\mathcal{V}^{\mathrm{a}}|} \right),
& 0 \leq &\theta \leq \pi, 
\label{eq:polar-ang}
\\
\varphi =& \tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}}
{\mathcal{V}^{\mathrm{ax}}} \right),
& 0 \leq &\varphi \leq 2\pi.
\label{eq:azimuthal-ang} 
\end{align}

\subsection{Fixing spin}\label{sec:theory-fixspin}
In a similar way we can fix in the $xy$ plane the spin direction along the $x$,
$y$, and $z$ directions and then define the magnitude of the spin velocity $|\mathcal{V}_{\sigma^{\mathrm{b}}}|$ in a fixed angle $\gamma_{b}$
\begin{align}
|\mathcal{V}_{\sigma^{\mathrm{b}}}| 
&=
\sqrt{
(\mathcal{V}^{\mathrm{ax}})^{2} +
(\mathcal{V}^{\mathrm{ay}})^{2} 
}, \\
\gamma_{\mathrm{b}} 
&=
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}}
{\mathcal{V}^{\mathrm{ax}}} \right),
\end{align}
where the angle is measured in the counter-clockwise direction from the positive
$x$ axis.

@@

@@

from evaluate Eq. \eqref{eq:va-mag} using different polarization angles $\alpha$

@@

For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
0.16\,eV where we found the most intense response for $\mathcal{V}^{\mathrm{x}}$
and $|\mathcal{V}^{\mathrm{y}}|$. In Fig. \ref{fig:up-3d-1} we present the
$\mathcal{V}^{\mathrm{a}}$ spectra resulting from evaluate again Eq. 
\eqref{eq:va-mag} using different polarization angles $\alpha$ in Eq.  
\eqref{eq:vab} but now for the C$_{16}$H$_{8}$-up structure. We can see that the
onset of the response is when the energy of the incoming light is the same of
the gap energy.
% 
From this picture we can see that for the zone between the energy range of
0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
$45^{\circ}$ is the zone where the maximum zone of response for both,
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ is hold.
% 
We found that the absolute maximum of the response is obtained when the
polarization angle is $\alpha=40^{\circ}$ and the energy of the incoming beam is
0.088\,eV.
%
In the top frames of  Figs. \ref{fig:up-vx-comp-rtp-1} and 
% 
\ref{fig:up-vy-comp-rtp-1} we present the results of
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ (left scale)
fixing the polarization angle to $\alpha=40^{\circ}$ for the \emph{up} structure
vs photon energy and the corresponding polar $\varphi$ and azimuthal $\theta$
angles (right scale). In the bottom frames of same figures we present the decomposition of
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ in the
corresponding $\mathcal{V}^{\mathrm{xx}}$, 
$\mathcal{V}^{\mathrm{xy}}$,
$\mathcal{V}^{\mathrm{xz}}$, and
$\mathcal{V}^{\mathrm{yx}}$, 
$\mathcal{V}^{\mathrm{yy}}$,
$\mathcal{V}^{\mathrm{yz}}$ 
components with $\alpha$ fixed to $40^{\circ}$. 
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vx-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vy-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
    structure. The local maximum response zone is localized for an energy range
    from 1.95\,eV to 2.00\,eV and for a polarization angle of the incoming beam
    from 25$^{\circ}$ to 50$^{\circ}$.}
    \label{fig:up-3d-2}
\end{figure}

@@

for the \emph{up} structure resulting from evaluate Eqns. \eqref{eq:va-mag} and

>>>>

\subsection{Fixing spin}\label{sec:theory-fixspin}
In a similar way we can fix in the $xy$ plane the spin direction along the $x$,
$y$, and $z$ directions and then define the magnitude of the spin velocity $|\mathcal{V}_{\sigma^{\mathrm{b}}}|$ in a fixed angle $\gamma_{b}$
\begin{align}
|\mathcal{V}_{\sigma^{\mathrm{b}}}| (\omega)
&=
\sqrt{
(\mathcal{V}^{\mathrm{ax}}(\omega))^{2}\ +
(\mathcal{V}^{\mathrm{ay}}(\omega))^{2}\ 
}, 
\label{eq:vs-mag}
\\
\gamma_{\mathrm{b}} (\omega)
&=
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega)}
{\mathcal{V}^{\mathrm{ax}}(\omega)} \right),
\label{eq:gamma-ang}
\end{align}
where the angle is measured in the counter-clockwise direction from the positive
$x$ axis.

@@

\subsection{Fixing velocity.}\label{sec:theory-fixvel}
Considering that we have 2D structures we fixed the velocity in the $xy$ plane
along $x$ and $y$ directions and we define $|\mathcal{V}^{\mathrm{a}}|$ as
\begin{equation}
|\mathcal{V}^{\mathrm{a}}| (\omega)= 
\sqrt {
(\mathcal{V}^{\mathrm{ax}}(\omega))^{2} +
(\mathcal{V}^{\mathrm{ay}}(\omega))^{2} +
(\mathcal{V}^{\mathrm{az}}(\omega))^{2} 
},
\label{eq:vv-mag}
\end{equation}
and the corresponding polar and azimuthal angles $\theta$ and $\varphi$ as
\begin{align}
\theta  (\omega)
=& 
\cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega)}
{|\mathcal{V}^{\mathrm{a}}(\omega)|} \right),
& 0 \leq &\theta \leq \pi, 
\label{eq:polar-ang}
\\
\varphi (\omega)
=& 
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega)}
{\mathcal{V}^{\mathrm{ax}}(\omega)} \right),
& 0 \leq &\varphi \leq 2\pi.
\label{eq:azimuthal-ang} 
\end{align}

\subsection{Layer-by-layer analysis.}\label{sec:theory-layer}

For a layered system we have that the total contribution of Eqns. 
\eqref{eq:vs-mag} and \eqref{eq:vv-mag} is given \cite{arzatePRB14} by

\begin{align}
|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega)|
=& 
\ell_{\mathrm{eff}}
\sum_{\ell=1}^{N_{\mathrm{eff}}}
|\mathcal{V}_{\sigma^{\mathrm{b}}} (\ell | \omega)|
\label{eq:vs-layer}
\\
|\mathcal{V}^{\mathrm{a}}(\omega)|
=&
\ell_{\mathrm{eff}}
\sum_{\ell=1}^{N_{\mathrm{eff}}}
|\mathcal{V}^{\mathrm{a}} (\ell | \omega)|
\label{eq:vv-layer}
\end{align}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin spin Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Fixing spin} % (fold)
\label{sec:res-fixspin}

% section res-fixspin (end)

@@

from evaluate Eq. \eqref{eq:vv-mag} using different polarization angles $\alpha$

@@

For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
0.16\,eV where we found the most intense response for $\mathcal{V}^{\mathrm{x}}$
and $|\mathcal{V}^{\mathrm{y}}|$. In Fig. \ref{fig:up-3d-1} we present the
$\mathcal{V}^{\mathrm{a}}$ spectra resulting from evaluate again Eq. 
\eqref{eq:vv-mag} using different polarization angles $\alpha$ in Eq.  
\eqref{eq:vab} but now for the C$_{16}$H$_{8}$-up structure. We can see that the
onset of the response is when the energy of the incoming light is the same of
the gap energy.
% 
From this picture we can see that for the zone between the energy range of
0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
$45^{\circ}$ is the zone where the maximum zone of response for both,
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ is hold.
% 
We found that the absolute maximum of the response is obtained when the
polarization angle is $\alpha=40^{\circ}$ and the energy of the incoming beam is
0.088\,eV.
%
In the top frames of  Figs. \ref{fig:up-vx-comp-rtp-1} and 
% 
\ref{fig:up-vy-comp-rtp-1} we present the results of
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ (left scale)
fixing the polarization angle to $\alpha=40^{\circ}$ for the \emph{up} structure
vs photon energy and the corresponding polar $\varphi$ and azimuthal $\theta$
angles (right scale). In the bottom frames of same figures we present the decomposition of
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ in the
corresponding $\mathcal{V}^{\mathrm{xx}}$, 
$\mathcal{V}^{\mathrm{xy}}$,
$\mathcal{V}^{\mathrm{xz}}$, and
$\mathcal{V}^{\mathrm{yx}}$, 
$\mathcal{V}^{\mathrm{yy}}$,
$\mathcal{V}^{\mathrm{yz}}$ 
components with $\alpha$ fixed to $40^{\circ}$. 
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vx-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vy-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
    structure. The local maximum response zone is localized for an energy range
    from 1.95\,eV to 2.00\,eV and for a polarization angle of the incoming beam
    from 25$^{\circ}$ to 50$^{\circ}$.}
    \label{fig:up-3d-2}
\end{figure}

@@

for the \emph{up} structure resulting from evaluate Eqns. \eqref{eq:vv-mag} and
